\tool

### 2018-02-21 paper/paper.tex
Intro done (don't change until comments)

Software is becoming more and more prevalent throughout our society. To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{---}, or \textit{software quality}. Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.

The 2017 Software Fail Watch by Tricentis, a software testing company, discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}. Studies also show the cost of fixing an error becomes more expensive the longer a bug exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created numerous software engineering tools to aid developers in their work. These tools automatically perform a wide variety of software development tasks to save time and effort for programmers. Research shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, code navigation, and more are beneficial for preventing errors and improving software quality. Ultimately, these useful tools can lead to reduced debugging costs and increased developer productivity.

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

@@

To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined how often recommendations were made and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

>>>>

Software is becoming increasingly prevalent in our society. To keep up with rising demands for technology, software engineers have made efforts to emphasize \textit{software quality}. Throughout the software development life cycle, companies focus on metric that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defective code remains a persisting and escalating problem.

The Software Fail Watch by Tricentis discovered that software failures impacted approximaltely half of the world's population (3.7 billion users) and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs in code, or debugging, is becoming increasingly time-consuming and costly.  A study by the National Institute of Standards and Technology reported that software engineers spend 70-80\% of their time debugging at work, and one error takes an average of 17.4 hours to debug~\cite{NIST}. Studies also show the cost of fixing an error becomes more expensive the longer it exists in source code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. These tools automatically perform a wide variety of software development tasks to save time and effort for programmers. The Software Engineering Body of Knowledge indicates the importance of development tools used to achieve ``desirable characteristics of software products'', noting they are part of defining software quality~\cite{SWEBOK}. Research shows tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, navigation, and more are useful for enhancing code. Ultimately, utilizing software enginering tools can lead to reduced debugging costs and increased developer productivity.

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve quality~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

@@

To answer these questions, we evaluated \tool~with \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:
